Are We Reusing Outdated and Licensed Code from Stack Overflow?

### 2017-02-12 cloneoverflow-latex/cloneoverflow.tex
A large update containing several changes (only abstract and conclusion is missing now).

\title{Are We Reusing Outdated and License-Violating Code from Stack Overflow?}

@@

\section{Introduction}
%The popularity of the Internet encourages tremendous amount of source code being shared online. 
Stack Overflow is a popular online programming community with 6.3 million users. It allows programmers to ask questions and give answers to programming problems. The website has found to be useful for software development \cite{Ponzanelli2013,Ponzanelli2014,Diamantopoulos2015,Keivanloo2014,Park2014, Stolee2014,Subramanian2013,Diamantopoulos2015,Treude2016} and also valuable for educational purposes \cite{Nasehi2012}. On Stack Overflow, each conversation contains a question and answer(s).  The answers frequently contain at least one code snippet as a solution to the question asked. The code snippet is usually not written directly on Stack Overflow website but copied from another location. It can be copied and modified from the problematic code snippet in the question, copied from an answerer's own code, or borrowed from other locations including open source software (OSS) systems. The process of posting and answering questions on Stack Overflow, which involves copying and pasting source code, can be considered as code cloning.

Code cloning is an activity of reusing source code by copying and pasting. It normally occurs in software development and account from 7\% to 23\% in typical software systems \cite{Bellon2007}. The benefits and drawbacks of clones are still controversial. Several authors state that clones lead to bug propagations and software maintenance issues \cite{Kamiya2002}, while some others have proofs that in some cases clones are not harmful than normal code or even beneficial \cite{Saini2016,Kapser2006}.

Code cloning can also have side effects of violating software licenses and software vulnerabilities. Carelessly cloning code from one project to another project with different license may cause software licensing violation \cite{German2009}. This also happens within the context of online Q\&A website such as Stack Overflow. An et al.~\cite{An2017} showed that 1,279 cloned snippets between Android apps and Stack Overflow have potential of violating software licenses. Security is also among the main concerns when code is copied from online source. Stack Overflow helps developers to solve Android programming problems more quickly than other resources while, at the same time, gives less secure code than books and the official Android documentation \cite{Acar2016}. Additionally, outdated and vulnerable third-party libraries from famous open source projects are cloned into in a large number of open source systems~\cite{Xia2014}.

@@

\subsection{Experimental Framework}
To answer the four research questions, we followed the experimental framework depicted in \Cref{fig:exp_framework}. We processed two datasets, Stack Overflow and 111 open source projects from Qualitas corpus. Java code snippets were extracted from Stack Overflow posts using regular expressions. We prepared Java code in both datasets by removing comments and pretty-printing to increase accuracy of clone detection. Then, we deployed two clone detection tools, Simian \cite{simian} and NiCad \cite{Roy2008,Cordy}, to locate clones between the two datasets. Due to scalability of Simian and NiCad, we partitioned the input and run the tools multiple times. Each run was composed of the whole Stack Overflow data and single Qualitas project. We repeated the process until we cover 111 projects.

We then converted the clone reports to General Clone Format (GCF)~\cite{Wang2013} and combined the 111 reports into a single GCF file. GCF provides a common format for clones which enabled us to reuse the same scripts to analyse clone reports from both Simian and NiCad. Moreover, using GCF, other additional clone detectors could be adopted, if needed, without any changes in the analysis. Simian did not provide an option to detect inter clones between two locations. Hence the Simian GCF clone report was pruned to contain only inter clone pairs between Stack Overflow and Qualitas projects. In this step, all intra clone pairs within either Stack Overflow or Qualitas were removed. NiCad provided an option to detect inter clones so no pruning is needed. We did not have an oracle of clones between the two data sets so we rely on a manual investigation to validate the reported clone candidates. However, the large amount of clone pairs hindered us from looking at all of them. Random sampling of clones could be done but may return mostly non-meaningful clones. Instead, we selected clone pair candidates by relying on agreement of clone detectors. If a clone pair was similarly reported by multiple tools, we had a higher confidence that it was a real clone pair. To achieve this, clone pairs from the two clone detectors were pair-wise matched to find agreements using Bellon's clone overlapping criteria \cite{Bellon2007}. This step generated \textbf{agreed clone pairs}. They were pairs with high confidence to be true clones since they obtained agreement from both tools. Then, pairs reported by Simian and NiCad that did not find agreement were \textbf{disagreed clone pairs}. The disagreed clone pairs were clones with less confidence than the agreed ones. Finally, agreed and disagreed clone pairs had been looked at manually by the first and the third author.

@@

\textbf{Stack Overflow}: we extracted Java code snippets from a snapshot of Stack Overflow dump \footnote{https://archive.org/details/stackexchange} in January 2016. The archived dump has a size of 9 gigabytes. The data dump was in XML format containing information of \textbf{Posts} (questions and answers) and supporting data such as user accounts and timestamps of the posts. We were interested in code snippets embedded in posts which were located between {\small\texttt{<code></code>}} tags. A Stack Overflow thread contains a post of question and several posts of answers. Every answer has voting score from its users. An answer can also be marked as \textbf{accepted answer} by the questioner if the solution fixes his/her problem. We collected Java code snippets using two criteria. First, we were only interested in code snippets with at least six lines. Snippets which were smaller than six lines were usually spurious clones \cite{Bellon2007}. Second, we only focused on code snippets in accepted answers. We chose the snippets in accept answers because they actually solved the problems in the questions and had a check mark sign on them to notify other users. Moreover, they were always displayed just below the questions which made them attractive to be reused than other answers. Each snippet was extracted from the dump using regular expressions and saved to a file using its post ID as the file's name. If an accepted answer had more than one code snippet, we appended an indexing number, starting from zero, after the post ID (e.g. 45051109\_0, and 45051109\_1.). Lastly, we added {\small\texttt{.java}} extension to the file's names so that clone detectors could recognise them. We finally obtained 144,075 Java code snippets which contain 2,347,269 lines of Java source code excluding comments and blank lines\footnote{Measured by cloc: https://github.com/AlDanial/cloc}.

\textbf{Open source systems}: we selected an established corpus for an empirical software engineering study called \textbf{Qualitas} \cite{QualitasCorpus} for this study. It is a curated Java corpus that has been used in several software engineering studies \cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}. The projects in the corpus represent various domains of software systems ranging from programming language to 3D and visualisation \cite{QualitasCorpus}. We selected the 20130901r release of Qualitas corpus containing 112 Java open source projects. This release contains projects with releases no later than 1st September 2013. We chose a snapshot late back in 2013 since we are interested in online code clones in the direction from open source projects to Stack Overflow. The 20130901r snapshot provides Java code that is at least 3 years old from the time of the experiment (January to December 2016). The time difference is sufficiently long for a number of code snippets to be copied onto Stack Overflow. Out of 112 Qualitas projects, there is one project, \texttt{jre}, that does not contain Java source code due to its licensing limitation \cite{QualitasCorpus} so it is removed from the study. This resulted in total of 111 projects analysed in the study. As shown in \Cref{tab:datasets}, the 111 Qualitas project have 160,937 Java files containing 19,086,883 lines of code. %Details of the 109 Qualitas projects and their licenses are listed in Table \ref{t:new_and_old}.

@@

\subsubsection{Clone Detectors}
There is a number of restrictions in terms of choosing clone detection tools for this study. First, they have to support Java. Second, due to nature of code snippets posted on Stack Overflow, some of them are not complete Java classes or methods. Hence, the tool must be flexible enough to process code snippets that are neither a complete block nor compilable. Third, since the amount of code that have to be processed are in a scale of millions line of code (as shown in \Cref{tab:datasets}), a clone detector must be scalable enough to successfully complete the execution and report clones in a reasonable amount of time. We have tried running 5 state-of-the-art clone detectors including Simian \cite{simian}, NiCad \cite{Cordy,Roy2008}, CCFinder \cite{Kamiya2002}, iClones \cite{Gode2009}, and DECKARD \cite{Jiang2007a} against Stack Overflow and Qualitas datasets. CCFinder, iClones, and DECKARD failed to report clones between 144,075 Stack Overflow code snippets and 111 Qualitas projects. All of them reported execution errors after running for couple of hours. Thus, we removed them from the study. Simian and NiCad completed the detection with success. We found that both of them are also flexible enough to handle code with incomplete methods or classes. %So, we decided to use both of them.

\textbf{Simian} is a text-based clone detector which locate clones at line-level granularity and has been used extensively in several clone studies \cite{Ragkhitwetsagul2016, Wang2013, Mondal2011, Cheung2015, Krinke2010}. It is a command-line tool which enables us to automate the detection. Furthermore, it offers normalisation of variable names and literals (strings, and numbers) which enable Simian to detect literal clones (type-1) and parameterised clones (type-2). \textbf{NiCad} is also a text-based clone detector which detects clones at either method- or block-level granularity. It can detect clones of type-1, 2 up to type-3 (clones with added/removed/relocated/changed statements) and is also used in several empirical clone studies \cite{Roy2008, Ragkhitwetsagul2016, Svajlenko2014, Wang2013, Mondal2011, Sajnani2016}. It utilises TXL \cite{Cordy2006} for parsing and pretty-printing source code. It also provide code normalisation by variable renaming and abstraction. We use a variant of NiCad called \textit{nicadcross}. It offers the same functionalities as the original NiCad but is specialised for detecting code clones between two systems. NiCad is also a command-line tool which makes it suitable for automation.

\subsubsection{Prioritise Clone Candidates Using Agreement}
A number of clones detected in large-scale datasets can be huge. In our study, there are totally 266,837,480 clone pairs reported. It is almost infeasible for human to manually validate them all. One can do a random sampling of clones. However, due to a very high number of false positives, they may end up looking at most of the false clones. Therefore, we adopted an idea of \textbf{clone agreement} which has been used in clone research studies \cite{Wang2013,Funaro2010,cr2016ssbse} in a situation that clone oracle is missing or impossible to establish. Clone pairs agreed by multiple clone detection tools have higher confident to be real clones \cite{cr2016ssbse}. By using this agreement-based approach, we could reduce the number of clone candidates for manual investigation by paying more attention to the ones agreed by multiple tools. To find an agreement between two clone pairs report by two different tools, we used clone pair matching metric proposed by Bellon et al.~\cite{Bellon2007}. Two clone pairs which have large enough overlapping clone lines can be categorised as either a good-match or an ok-match pair (denoted as \textit{good} and \textit{ok} respectively) with a confident value between 0 and 1. A \textit{good} clone pair has stronger agreement than an \textit{ok} pair. We follow the following definitions of good- and ok-match introduced in the original paper.

@@

\subsection{Clone Detector's Parameter Tuning}
We were aware of effects of configurations to clone detection results and the importance of searching for optimised configurations in empirical clone studies \cite{Wang2014,cr2016ssbse,Ragkhitwetsagul2016,Svajlenko2014}. However, considering the massive size of the two datasets and search space of at least 15 Simian's and 5 NiCad's parameters, we were hindered from searching for the best configurations of the tools. Thus, we decided to configure Simian and NiCad using two established configurations: 1) the tools' default configurations chosen by the tools' creators (denoted as \textit{D}), and 2) the discovered configurations for Bellon's Java projects from \textit{EvaClone}, a study of optimising clone detectors' configurations based on clone agreement, by Wang et al.~\cite{Wang2013} (denoted by \textit{E}). The details of the two configurations are described in \Cref{t:param_tuning}. Having two clone detectors, Simian (denoted as \textit{S}) and NiCad (denoted as \textit{N}), with two chosen configurations each, we looked for Bellon's good and ok-match in four possible pair-wise combinations: $S_{D}N_{D}$, $S_{D}N_{E}$, $S_{E}N_{D}$, and $S_{E}N_{E}$.

@@

The clone statistics obtained from running Simian and NiCad with \textit{D} and \textit{E} configurations are presented in \Cref{tab:raw_stats}. From \Cref{tab:raw_stats}, Simian clones cover approximately 1\% of the 144,075 Stack Overflow snippets, 1,086 reported by $S_D$ and 1,531 from $S_E$ respectively. $N_D$ reports clones in 1,392 Stack Overflow code snippets, while $N_E$ reports clones in a larger number of 12,886 snippets  mainly due to its relaxed configurations. In terms of number of clone pairs, $S_E$ and $N_E$ report a large number of clone pairs of 63,635,844 and 251,449,849 respectively. This is expected since EvaClone configurations prefer recall so it tends to remote more clones \cite{Wang2013}. The average clone size of $S_D$ is 7.72 lines which is bigger than its $S_E$ counterpart of 4.79. Similarly, $N_D$ has an average clone size of 9.84 lines which is bigger than 5.33 reported by $N_E$. We can see from the statistics that EvaClone tunes the tools in the way that they report smaller clones. The average percentage of Stack Overflow code snippets that are cloned according to $S_D$, $S_E$, $N_D$, and $N_E$ is 29\%, 28\%, 25\%, and 21\% accordingly. A quick manual check of Simian's clone report revealed that there were problematic 11 snippets. These 11 snippets triggered Simian to generate large clone clusters containing a huge number of false clones from array initialisation. Hence, their clones were removed from further analyses.

@@

Agreed clone pairs are clone pairs that pass Bellon's good- or ok-match criteria and selected for manual investigation. Similar to the original study, we select a threshold \textit{p} of 0.7 for both \textit{good} and \textit{ok} pairs \cite{Bellon2007}. %The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}. 
We encountered NiCad failures with a few Qualitas projects.~$N_D$ could not detect clones in \texttt{hibernate} due to clustering errors. $N_E$ generated renaming errors for 5 projects including \texttt{vuze}, \texttt{hibernate}, \texttt{myfaces}, \texttt{netbeans}, and \texttt{spring}. We had contacted the creator of NiCad regarding the issues. They identified them as problems of long file paths and TXL grammars which will be fixed in the next NiCad releases. As a result, we did not have NiCad clones from these projects in the agreed clone pairs. Simian clones of the same projects also disappeared from the agreed clone pairs since they could not find matches.

@@

Even choosing only the default configurations, the number of clone pair candidates are still very large for manual inspection (67,570 for $S_D$ and 229,176 pairs for $N_D$). We hence apply four filters: \textbf{clone size, regular expression, similarity threshold, and good/ok pairs}. For the clone size filter, we raise the minimum clone size to 10 line as larger clones tend to be more interesting while smaller ones tend to be false clones \cite{Saini2016}. Moreover, Gabel and Su show that unique code tend to be larger than seven lines \cite{Gabel2010}. The 10--line threshold is already the default configuration for NiCad, thus this filter affects Simian clones only (Simian's default configurations consider a minimum of 6 lines).~The regular expression filter captures uninteresting boiler-plate clones of \verb|hashCode()| methods and some of the obvious getters and setters using regular expressions and removes them. The third filter, similarity threshold, applies only to NiCad clone pairs since Simian does not provide this similarity threshold configuration. The last filter, good/ok pairs, filters the pairs that already exist in \textit{good} or \textit{ok} set to avoid duplicates.

@@

\textbf{EX: External Sources.} We found 178 online clone pairs with evidences of cloning from external sources to Stack Overflow. They include 4, 23, 145, and 6 pairs from \textit{good}, \textit{ok}, $S_D$, and $N_D$ set respectively.
%\begin{table}[]
%	\centering
%	\caption{31 external clones found in Stack Overflow posts}
%	\label{tab:ext_clones}
%	\begin{tabular}{l|r|r}
%		\hline
%		Type        & FOSS & Web \\ \hline
%		StackOverflow only     & 1    & 1   \\
%		StackOverflow + Qualitas & 15   & 14  \\ \hline
%	\end{tabular}
%\end{table}
This findings complement a study of inter clones between software projects \cite{Svajlenko2014}. We show that, besides software projects, clones can also be copied over different websites on the Internet. There are 15 clone pairs that are originated from programming websites. For example, we found a clone of code snippet to convert numbers into words which is copied from www.rgagnon.com/javadetails/java-0426.html. Both Stack Overflow and {\small\texttt{compiere}} project source code contain attribution to the original source. Another example is a code of algorithm to generate graphical \textit{Perlin noise} copied from http://mrl.nyu.edu/\textasciitilde perlin/noise/. This code is used in both Stack Overflow and {\small\texttt{aoi}} project with attribution. %The original code of the 15 clone pairs do not have licensing information so these clones do not violate any license. 
There were 12 pairs cloned from {\small\texttt{zxing}}, {\small\texttt{jasper}}, {\small\texttt{java.util}}, {\small\texttt{javax.servlet}}, and {\small\texttt{org.bouncycastle.crypto}} project.

@@

\begin{table}
	\centering
	\caption{Classification results of agreed and disagreed clone pairs.}
	\label{tab:classification_good_o}
	\small
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{l|r|r|r|r|r|r|r|r}
			\hline
			Set & QS & SQ & UD & EX & BP & IN & AC & Total \\ 
			\hline
			\multirow{1}{*}{\textit{good}}  & 3 & 0 & 11 & 4 & 111  & 7 & 2,172 & 2,308 \\
			\multirow{1}{*}{\textit{ok}}  & 14 & 0 & 40 & 21 & 11,547 & 22 & 105 & 11,749 \\
			\multirow{1}{*}{$S_D$} & 86 & 0 & 294 & 145 & 17,074 & 74 & 128 & 17,801 \\
			\multirow{1}{*}{$N_D$} & 9  & 0 & 35 & 6 & 17 & 8 & 13 & 88 \\ 
			\hline
			Total & 112 & 0 & 380 & 176 & 28,749 & 111 & 2,418 & 31,946 \\ 
			\hline
		\end{tabular} 
	}
\end{table}

@@

%\subsubsection{Outdated Clones}
To the best of our knowledge, this work is the first to discuss a problem of outdated code on Stack Overflow. Outdated code occurs when a piece of code has been copied from its origin to another location and later the original code has been updated \cite{Xia2014}. Usually code clone detection is used to locate clone instances and update them to match with the original code \cite{Bellon2007}. However, for online code clones, the clones are pervasive and are more difficult to detect than in a local project(s) due to its large search space and the mix of natural and programming language combined together in Stack Overflow posts. Moreover, Stack Overflow is not a software. There is no test suite to run and check whether the code snippets are still working as expected.

>>>>

\title{Are We Reusing Outdated and Licensed Code from Stack Overflow?}

@@

\section{Introduction}
%The popularity of the Internet encourages tremendous amount of source code being shared online. 
Stack Overflow is a popular online programming community with 6.3 million users. It allows programmers to ask questions and give answers to programming problems. The website has found to be useful for software development~\cite{Ponzanelli2013,Ponzanelli2014,Diamantopoulos2015,Keivanloo2014,Park2014, Stolee2014,Subramanian2013,Diamantopoulos2015,Treude2016} and also valuable for educational purposes~\cite{Nasehi2012}. On Stack Overflow, each conversation contains a question and answer(s).  The answers frequently contain at least one code snippet as a solution to the question asked. The code snippet is usually not written directly on Stack Overflow website but copied from another location. It can be copied and modified from the problematic code snippet in the question, copied from an answerer's own code, or borrowed from other locations including open source software (OSS) systems. The process of posting and answering questions on Stack Overflow, which involves copying and pasting source code, can be considered as code cloning.

Code cloning is an activity of reusing source code by copying and pasting. It normally occurs in software development and account from 7\% to 23\% in typical software systems~\cite{Bellon2007}. The benefits and drawbacks of clones are still controversial. Several authors state that clones lead to bug propagations and software maintenance issues~\cite{Kamiya2002}, while some others have proofs that in some cases clones are not harmful than normal code or even beneficial~\cite{Saini2016,Kapser2006}.

Code cloning can also have side effects of violating software licenses and software vulnerabilities. Carelessly cloning code from one project to another project with different license may cause software licensing violation~\cite{German2009}. This also happens within the context of online Q\&A website such as Stack Overflow. An et al.~\cite{An2017} showed that 1,279 cloned snippets between Android apps and Stack Overflow have potential of violating software licenses. Security is also among the main concerns when code is copied from online source. Stack Overflow helps developers to solve Android programming problems more quickly than other resources while, at the same time, gives less secure code than books and the official Android documentation~\cite{Acar2016}. Additionally, outdated and vulnerable third-party libraries from famous open source projects are cloned into in a large number of open source systems~\cite{Xia2014}.

@@

\subsection{Experimental Framework}
To answer the four research questions, we followed the experimental framework depicted in \Cref{fig:exp_framework}. We processed two datasets, Stack Overflow and 111 open source projects from Qualitas corpus. Java code snippets were extracted from Stack Overflow posts using regular expressions. We prepared Java code in both datasets by removing comments and pretty-printing to increase accuracy of clone detection. Then, we deployed two clone detection tools, Simian~\cite{simian} and NiCad~\cite{Roy2008,Cordy}, to locate clones between the two datasets. Due to scalability of Simian and NiCad, we partitioned the input and run the tools multiple times. Each run was composed of the whole Stack Overflow data and single Qualitas project. We repeated the process until we cover 111 projects.

We then converted the clone reports to General Clone Format (GCF)~\cite{Wang2013} and combined the 111 reports into a single GCF file. GCF provides a common format for clones which enabled us to reuse the same scripts to analyse clone reports from both Simian and NiCad. Moreover, using GCF, other additional clone detectors could be adopted, if needed, without any changes in the analysis. Simian did not provide an option to detect inter clones between two locations. Hence the Simian GCF clone report was pruned to contain only inter clone pairs between Stack Overflow and Qualitas projects. In this step, all intra clone pairs within either Stack Overflow or Qualitas were removed. NiCad provided an option to detect inter clones so no pruning is needed. We did not have an oracle of clones between the two data sets so we rely on a manual investigation to validate the reported clone candidates. However, the large amount of clone pairs hindered us from looking at all of them. Random sampling of clones could be done but may return mostly non-meaningful clones. Instead, we selected clone pair candidates by relying on agreement of clone detectors. If a clone pair was similarly reported by multiple tools, we had a higher confidence that it was a real clone pair. To achieve this, clone pairs from the two clone detectors were pair-wise matched to find agreements using Bellon's clone overlapping criteria~\cite{Bellon2007}. This step generated \textbf{agreed clone pairs}. They were pairs with high confidence to be true clones since they obtained agreement from both tools. Then, pairs reported by Simian and NiCad that did not find agreement were \textbf{disagreed clone pairs}. The disagreed clone pairs were clones with less confidence than the agreed ones. Finally, agreed and disagreed clone pairs had been looked at manually by the first and the third author.

@@

\textbf{Stack Overflow}: we extracted Java code snippets from a snapshot of Stack Overflow dump \footnote{https://archive.org/details/stackexchange} in January 2016. The archived dump has a size of 9 gigabytes. The data dump was in XML format containing information of \textbf{Posts} (questions and answers) and supporting data such as user accounts and timestamps of the posts. We were interested in code snippets embedded in posts which were located between {\small\texttt{<code></code>}} tags. A Stack Overflow thread contains a post of question and several posts of answers. Every answer has voting score from its users. An answer can also be marked as \textbf{accepted answer} by the questioner if the solution fixes his/her problem. We collected Java code snippets using two criteria. First, we were only interested in code snippets with at least six lines. Snippets which were smaller than six lines were usually spurious clones~\cite{Bellon2007}. Second, we only focused on code snippets in accepted answers. We chose the snippets in accept answers because they actually solved the problems in the questions and had a check mark sign on them to notify other users. Moreover, they were always displayed just below the questions which made them attractive to be reused than other answers. Each snippet was extracted from the dump using regular expressions and saved to a file using its post ID as the file's name. If an accepted answer had more than one code snippet, we appended an indexing number, starting from zero, after the post ID (e.g. 45051109\_0, and 45051109\_1.). Lastly, we added {\small\texttt{.java}} extension to the file's names so that clone detectors could recognise them. We finally obtained 144,075 Java code snippets which contain 2,347,269 lines of Java source code excluding comments and blank lines\footnote{Measured by cloc: https://github.com/AlDanial/cloc}.

\textbf{Open source systems}: we selected an established corpus for an empirical software engineering study called \textbf{Qualitas}~\cite{QualitasCorpus} for this study. It is a curated Java corpus that has been used in several software engineering studies~\cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}. The projects in the corpus represent various domains of software systems ranging from programming language to 3D and visualisation~\cite{QualitasCorpus}. We selected the 20130901r release of Qualitas corpus containing 112 Java open source projects. This release contains projects with releases no later than 1st September 2013. We chose a snapshot late back in 2013 since we are interested in online code clones in the direction from open source projects to Stack Overflow. The 20130901r snapshot provides Java code that is at least 3 years old from the time of the experiment (January to December 2016). The time difference is sufficiently long for a number of code snippets to be copied onto Stack Overflow. Out of 112 Qualitas projects, there is one project, \texttt{jre}, that does not contain Java source code due to its licensing limitation~\cite{QualitasCorpus} so it is removed from the study. This resulted in total of 111 projects analysed in the study. As shown in \Cref{tab:datasets}, the 111 Qualitas project have 160,937 Java files containing 19,086,883 lines of code. %Details of the 109 Qualitas projects and their licenses are listed in Table \ref{t:new_and_old}.

@@

\subsubsection{Clone Detectors}
There is a number of restrictions in terms of choosing clone detection tools for this study. First, they have to support Java. Second, due to nature of code snippets posted on Stack Overflow, some of them are not complete Java classes or methods. Hence, the tool must be flexible enough to process code snippets that are neither a complete block nor compilable. Third, since the amount of code that have to be processed are in a scale of millions line of code (as shown in \Cref{tab:datasets}), a clone detector must be scalable enough to successfully complete the execution and report clones in a reasonable amount of time. We have tried running 5 state-of-the-art clone detectors including Simian~\cite{simian}, NiCad~\cite{Cordy,Roy2008}, CCFinder~\cite{Kamiya2002}, iClones~\cite{Gode2009}, and DECKARD~\cite{Jiang2007a} against Stack Overflow and Qualitas datasets. CCFinder, iClones, and DECKARD failed to report clones between 144,075 Stack Overflow code snippets and 111 Qualitas projects. All of them reported execution errors after running for couple of hours. Thus, we removed them from the study. Simian and NiCad completed the detection with success. We found that both of them are also flexible enough to handle code with incomplete methods or classes. %So, we decided to use both of them.

\textbf{Simian} is a text-based clone detector which locate clones at line-level granularity and has been used extensively in several clone studies~\cite{Ragkhitwetsagul2016, Wang2013, Mondal2011, Cheung2015, Krinke2010}. It is a command-line tool which enables us to automate the detection. Furthermore, it offers normalisation of variable names and literals (strings, and numbers) which enable Simian to detect literal clones (type-1) and parameterised clones (type-2). \textbf{NiCad} is also a text-based clone detector which detects clones at either method- or block-level granularity. It can detect clones of type-1, 2 up to type-3 (clones with added/removed/relocated/changed statements) and is also used in several empirical clone studies~\cite{Roy2008, Ragkhitwetsagul2016, Svajlenko2014, Wang2013, Mondal2011, Sajnani2016}. It utilises TXL~\cite{Cordy2006} for parsing and pretty-printing source code. It also provide code normalisation by variable renaming and abstraction. We use a variant of NiCad called \textit{nicadcross}. It offers the same functionalities as the original NiCad but is specialised for detecting code clones between two systems. NiCad is also a command-line tool which makes it suitable for automation.

\subsubsection{Prioritise Clone Candidates Using Agreement}
A number of clones detected in large-scale datasets can be huge. In our study, there are totally 266,837,480 clone pairs reported. It is almost infeasible for human to manually validate them all. One can do a random sampling of clones. However, due to a very high number of false positives, they may end up looking at most of the false clones. Therefore, we adopted an idea of \textbf{clone agreement} which has been used in clone research studies~\cite{Wang2013,Funaro2010,cr2016ssbse} in a situation that clone oracle is missing or impossible to establish. Clone pairs agreed by multiple clone detection tools have higher confident to be real clones~\cite{cr2016ssbse}. By using this agreement-based approach, we could reduce the number of clone candidates for manual investigation by paying more attention to the ones agreed by multiple tools. To find an agreement between two clone pairs report by two different tools, we used clone pair matching metric proposed by Bellon et al.~\cite{Bellon2007}. Two clone pairs which have large enough overlapping clone lines can be categorised as either a good-match or an ok-match pair (denoted as \textit{good} and \textit{ok} respectively) with a confident value between 0 and 1. A \textit{good} clone pair has stronger agreement than an \textit{ok} pair. We follow the following definitions of good- and ok-match introduced in the original paper.

@@

\subsection{Clone Detector's Parameter Tuning}
We were aware of effects of configurations to clone detection results and the importance of searching for optimised configurations in empirical clone studies~\cite{Wang2014,cr2016ssbse,Ragkhitwetsagul2016,Svajlenko2014}. However, considering the massive size of the two datasets and search space of at least 15 Simian's and 5 NiCad's parameters, we were hindered from searching for the best configurations of the tools. Thus, we decided to configure Simian and NiCad using two established configurations: 1) the tools' default configurations chosen by the tools' creators (denoted as \textit{D}), and 2) the discovered configurations for Bellon's Java projects from \textit{EvaClone}, a study of optimising clone detectors' configurations based on clone agreement, by Wang et al.~\cite{Wang2013} (denoted by \textit{E}). The details of the two configurations are described in \Cref{t:param_tuning}. Having two clone detectors, Simian (denoted as \textit{S}) and NiCad (denoted as \textit{N}), with two chosen configurations each, we looked for Bellon's good and ok-match in four possible pair-wise combinations: $S_{D}N_{D}$, $S_{D}N_{E}$, $S_{E}N_{D}$, and $S_{E}N_{E}$.

@@

The clone statistics obtained from running Simian and NiCad with \textit{D} and \textit{E} configurations are presented in \Cref{tab:raw_stats}. From \Cref{tab:raw_stats}, Simian clones cover approximately 1\% of the 144,075 Stack Overflow snippets, 1,086 reported by $S_D$ and 1,531 from $S_E$ respectively. $N_D$ reports clones in 1,392 Stack Overflow code snippets, while $N_E$ reports clones in a larger number of 12,886 snippets  mainly due to its relaxed configurations. In terms of number of clone pairs, $S_E$ and $N_E$ report a large number of clone pairs of 63,635,844 and 251,449,849 respectively. This is expected since EvaClone configurations prefer recall so it tends to remote more clones~\cite{Wang2013}. The average clone size of $S_D$ is 7.72 lines which is bigger than its $S_E$ counterpart of 4.79. Similarly, $N_D$ has an average clone size of 9.84 lines which is bigger than 5.33 reported by $N_E$. We can see from the statistics that EvaClone tunes the tools in the way that they report smaller clones. The average percentage of Stack Overflow code snippets that are cloned according to $S_D$, $S_E$, $N_D$, and $N_E$ is 29\%, 28\%, 25\%, and 21\% accordingly. A quick manual check of Simian's clone report revealed that there were problematic 11 snippets. These 11 snippets triggered Simian to generate large clone clusters containing a huge number of false clones from array initialisation. Hence, their clones were removed from further analyses.

@@

Agreed clone pairs are clone pairs that pass Bellon's good- or ok-match criteria and selected for manual investigation. Similar to the original study, we select a threshold \textit{p} of 0.7 for both \textit{good} and \textit{ok} pairs~\cite{Bellon2007}. %The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}. 
We encountered NiCad failures with a few Qualitas projects.~$N_D$ could not detect clones in \texttt{hibernate} due to clustering errors. $N_E$ generated renaming errors for 5 projects including \texttt{vuze}, \texttt{hibernate}, \texttt{myfaces}, \texttt{netbeans}, and \texttt{spring}. We had contacted the creator of NiCad regarding the issues. They identified them as problems of long file paths and TXL grammars which will be fixed in the next NiCad releases. As a result, we did not have NiCad clones from these projects in the agreed clone pairs. Simian clones of the same projects also disappeared from the agreed clone pairs since they could not find matches.

@@

Even choosing only the default configurations, the number of clone pair candidates are still very large for manual inspection (67,570 for $S_D$ and 229,176 pairs for $N_D$). We hence apply four filters: \textbf{clone size, regular expression, similarity threshold, and good/ok pairs}. For the clone size filter, we raise the minimum clone size to 10 line as larger clones tend to be more interesting while smaller ones tend to be false clones~\cite{Saini2016}. Moreover, Gabel and Su show that unique code tend to be larger than seven lines~\cite{Gabel2010}. The 10--line threshold is already the default configuration for NiCad, thus this filter affects Simian clones only (Simian's default configurations consider a minimum of 6 lines).~The regular expression filter captures uninteresting boiler-plate clones of \verb|hashCode()| methods and some of the obvious getters and setters using regular expressions and removes them. The third filter, similarity threshold, applies only to NiCad clone pairs since Simian does not provide this similarity threshold configuration. The last filter, good/ok pairs, filters the pairs that already exist in \textit{good} or \textit{ok} set to avoid duplicates.

@@

\textbf{EX: External Sources.} We found 178 online clone pairs with evidences of cloning from external sources to Stack Overflow. They include 4, 23, 145, and 6 pairs from \textit{good}, \textit{ok}, $S_D$, and $N_D$ set respectively.
%\begin{table}[]
%	\centering
%	\caption{31 external clones found in Stack Overflow posts}
%	\label{tab:ext_clones}
%	\begin{tabular}{l|r|r}
%		\hline
%		Type        & FOSS & Web \\ \hline
%		StackOverflow only     & 1    & 1   \\
%		StackOverflow + Qualitas & 15   & 14  \\ \hline
%	\end{tabular}
%\end{table}
This findings complement a study of inter clones between software projects~\cite{Svajlenko2014}. We show that, besides software projects, clones can also be copied over different websites on the Internet. There are 15 clone pairs that are originated from programming websites. For example, we found a clone of code snippet to convert numbers into words which is copied from www.rgagnon.com/javadetails/java-0426.html. Both Stack Overflow and {\small\texttt{compiere}} project source code contain attribution to the original source. Another example is a code of algorithm to generate graphical \textit{Perlin noise} copied from http://mrl.nyu.edu/\textasciitilde perlin/noise/. This code is used in both Stack Overflow and {\small\texttt{aoi}} project with attribution. %The original code of the 15 clone pairs do not have licensing information so these clones do not violate any license. 
There were 12 pairs cloned from {\small\texttt{zxing}}, {\small\texttt{jasper}}, {\small\texttt{java.util}}, {\small\texttt{javax.servlet}}, and {\small\texttt{org.bouncycastle.crypto}} project.

@@

\begin{table}
	\centering
	\caption{Classification results of agreed and disagreed clone pairs.}
	\label{tab:classification_good_o}
	\small
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{l|r|r|r|r|r|r|r|r}
			\hline
			Set & QS & SQ & UD & EX & BP & IN & AC & Total \\ 
			\hline
			\multirow{1}{*}{\textit{good}}  & 3 & 0 & 11 & 4 & 111  & 7 & 2,172 & 2,308 \\
			\multirow{1}{*}{\textit{ok}}  & 14 & 0 & 20 & 41 & 11,547 & 22 & 105 & 11,749 \\
			\multirow{1}{*}{$S_D$} & 86 & 0 & 293 & 146 & 17,074 & 74 & 128 & 17,801 \\
			\multirow{1}{*}{$N_D$} & 9  & 0 & 35 & 6 & 17 & 8 & 13 & 88 \\ 
			\hline
			Total & 112 & 0 & 359 & 197 & 28,749 & 111 & 2,418 & 31,946 \\ 
			\hline
		\end{tabular} 
	}
\end{table}

@@

%\subsubsection{Outdated Clones}
To the best of our knowledge, this work is the first to discuss a problem of outdated code on Stack Overflow. Outdated code occurs when a piece of code has been copied from its origin to another location and later the original code has been updated~\cite{Xia2014}. Usually code clone detection is used to locate clone instances and update them to match with the original code~\cite{Bellon2007}. However, for online code clones, the clones are pervasive and are more difficult to detect than in a local project(s) due to its large search space and the mix of natural and programming language combined together in Stack Overflow posts. Moreover, Stack Overflow is not a software. There is no test suite to run and check whether the code snippets are still working as expected.
